Practical seed-recovery for the PCG Pseudo-Random Number Generator

### 2020-08-19 article/main.tex
hiddennumberprobleme

We will be facing a ``high-dimension'' instance in section~\ref{sec:big_cvp}
and many ``low-dimension'' in sections~\ref{sec:Cknown}
and~\ref{sec:Cunknown}. The rest of this section discusses algorithmic tools to
solve these problems. We first claim that $2^{k-t} \widetilde{T}$ is
``close'' to a point of the lattice $\mathcal{L}$.

>>>>

This is a particular case of the hidden number problem. We will be facing a ``high-dimension'' instance in section~\ref{sec:big_cvp}
and many ``low-dimension'' instances in sections~\ref{sec:Cknown}
and~\ref{sec:Cunknown}. The rest of this section discusses algorithmic tools to
solve these problems. We first claim that $2^{k-t} \widetilde{T}$ is
``close'' to a point of the lattice $\mathcal{L}$.
